Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-30 parts/intro.tex
move appendix eplanation back to chapt1
z errors

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{img/timelapse3}
  \caption{Amount of generated models over time, since an arb. starting point; top Figure shows all models, bottom Figure shows 5 selected candidates with most activity. 8 users contributed more than five models. }
  \label{fig:time}
\end{figure}

The volunteers were encouraged to create models of objects found in Space~Warps before they were classified as plausible candidates.
Figure~\ref{fig:time} shows the evolution of the total number of models the users generated, but only for the candidates, models created for system that turned out to be non candidates were not counted.
The first beta version of SpaghettiLens was launched around day 140 and was tested and improved on the fly.
It saw 8 volunteers with major contributions.
At day 820 the first full version of SpaghettiLens was presented online, around the same time the list of identified candidates was available.
Around day 200 the volunteers started a modelling challenge for the candidate later to be identified as SW01.
65 days later 30 models have been created for this particular and this group converged to a set of favorite models that they presented in an online letter.
